A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-10-02 rr-flow.Rmd
add redoc, solve #44

In our own experience, it is often not possible to convince all co-authors to switch to a different document processing environment, such as RMarkdown. That is, we have experienced that after writing up the first draft in Rmarkdown, one must eventually switch to a dynamically generated Word-file that is from then on used as static file that is used as basis for multiple iterations among the co-authors. This means, that ideally, one would have to manually merge the final Word file back to the RMarkdown souce, which generally is only possible manually. But we believe that even if this final step does not happen that - as long as dynamically generated elements are not manipulated - ensuring the reproducibility of the analysis and the initial draft is a big step forward. Making such static Word-file more dynamic is is possible with the officer package [@gohel2019officer], which allows the manipulation of  Word (.docx) and PowerPoint (.pptx) documents. That is, given a formatted static template file, one can dynamically paste images, tables and text into documents from R. We consider such static file with dynamic content, less elegant but potentially more practical, when not all authors can adhere to the described process.

>>>>

In our own experience, it is often not possible to convince all co-authors to switch to a different document processing environment, such as RMarkdown. That is, we have experienced that after writing up the first draft in Rmarkdown, one must eventually to genereate a Word-file that is from then on used as static file serving as a basis for multiple iterations among the co-authors. Reteining reproduciblity in such situation requires tediues manuel synchronization. This labor can be saved with the [rodoc package](https://noamross.github.io/redoc/articles/mixed-workflows-with-redoc.html), which enables a two-way workflow between Word and Rmarkdown. The conversion between Rmarkdown and Word retains all changes and even supports tracked changes. We consider such workflow less elegant since changes can be hard to track in git, but potentially more practical, when not all authors can adhere to the described process.
